\documentclass[11pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1in,headheight=15pt]{geometry}

% MATH
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage[short]{optidef}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% FORMATTING
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!80!black},
    urlcolor={blue!60!black}
}
\usepackage{float}
\usepackage{booktabs}

% Multi-File Structure
\usepackage{subfiles}
\graphicspath{{images/}{../images/}}

% FONT
% http://www.tug.dk/FontCatalogue/fbb/
% add command here
\usepackage[T1]{fontenc}
\usepackage{fbb}

% DEFNS
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{Definition}

\newcommand{\one}{\mathbf{1}}
\newcommand{\var}{\mathbf{\text{var}}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\defeq}{\overset{\text{def}}{=}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\lim}[1]{\underset{#1}{\text{lim}} \ }
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\min}[1]{\underset{#1}{\text{min}} \ }
\renewcommand{\max}[1]{\underset{#1}{\text{max}} \ }
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}


% SETTINGS

% fancyhdr setting (adds header)
\pagestyle{fancy}

\graphicspath{ {images/} {../images/} }


% FOR TITLE/ABSTRACT PAGES

% hack to show copyright if you use a non-default font
\renewcommand*\copyright{\textcopyright}

\title{Title}
\author{Zachary D. Blanks}
\date{June, 2019}

\def\permission{\par\noindent{\centering
   The author hereby grants to MIT and DRAPER permission to reproduce and to
   distribute publicly paper and electronic copies of this thesis
   document in whole or in part in any medium now known or hereafter
   created.}\par
}

\def\signature#1#2{\par\noindent#1\dotfill\null\\*
  {\raggedleft #2\par}
}

\def\blankpage{
	\newpage
	\thispagestyle{plain}
	\topskip0pt
	\vspace*{\fill}
	\begin{center} THIS PAGE INTENTIONALLY LEFT BLANK\end{center}
	\vspace*{\fill}
	\newpage
}

% hack to allow use of \@title, \@author, ... macros
\makeatletter

%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%
%  TITLE   %
%%%%%%%%%%%%

\thispagestyle{plain}
{
	\centering%
	\vfill
	{\Large\bf\@title}\par%
	\vspace{0.5cm}
	by\par%
	\vspace{0.5cm}
	{\Large\@author}\par%
	\vspace{0.5cm}%
	B.S. Operations Research, United States Air Force Academy\par%
	\vspace{0.5cm}%
	Submitted to the Sloan School of Management \\%
	in partial fulfillment of the requirements for the degree of\par %
	\vspace{0.5cm}%
	Master of Science in Operations Research\par%
	\vspace{0.5cm}%
	at the\par%
	\vspace{0.5cm}%
	MASSACHUSETTS INSTITUTE OF TECHNOLOGY\par
	\vspace{0.5cm}%
	\@date\par%
	\vspace{0.5cm}%
	\copyright \ \ \@author, 2019.  All rights reserved.\par%
	\vspace{0.5cm}%
	\permission\par
	\vspace{0.5cm}%
	\vskip 3\baselineskip%
	\signature{Author}{Sloan School of Management \\ May 18, 2017}%
	\vspace{0.75cm}%
	\signature{Certified by}{Dr. Troy M. Lau \\ 
	The Charles Stark Draper Laboratory \\ 
	Technical Supervisor}
	\vspace{0.75cm}%
	\signature{Certified by}{Prof. Rahul Mazumder \\ 
	Assistant Professor of Operations Research and Statistics \\ 
	Thesis Supervisor}%
	\vspace{0.75cm}%
	\signature{Accepted by}{Prof. Dimitris Bertsimas \\ 
	Boeing Professor of Operations Research \\
	Co-Director, Operations Research Center}%
	\vfill
}

%%%%%%%

\blankpage

%%%%%%%%%%%%
% ABSTRACT %
%%%%%%%%%%%%

\thispagestyle{plain}
{
	\centering%
	\vfill
	{\Large\bf \@title}\par%
	\vspace{0.5cm}
	by\par%
	\vspace{0.5cm}
	{\Large \@author}\par%
	\vspace{1cm}%
	Submitted to the Sloan School of Management \\
	on May 18, 2017 in partial fulfillment of the \\
	requirements for the degree of \\ 
	Master of Science in Operations Research\par%
	\vspace{1cm}
}

{\noindent{\Large\bf Abstract}}\par
\vspace{0.5cm}
{\noindent 
Abstract abstract abstract.
}\par
\vspace{1cm}

{\noindent
Technical Supervisor: Dr. Troy M. Lau \\
The Charles Stark Draper Laboratory
}\par
\vspace{0.5cm}
{\noindent
Thesis Supervisor: Prof. Rahul Mazumder \\
Assistant Professor of Operations Research and Statistics
}
\vfill

%%%%%%%%%

\blankpage

%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGEMENTS %
%%%%%%%%%%%%%%%%%%%%

\chapter*{Acknowledgements}
I want to thank...


%%%%%%%%%%%%

\onehalfspacing

\tableofcontents

\listoffigures

\subfile{chapters/introduction}
\subfile{chapters/chapter2}
\subfile{chapters/chapter3}
\subfile{chapters/chapter4}
\subfile{chapters/chapter5}
\subfile{chapters/conclusion}


\bibliographystyle{abbrv}
\nocite{ilya_flyamer_2018_1494343}
\bibliography{references1}

\appendix
\subfile{chapters/appendix1}
\subfile{chapters/cifar}

\end{document}